Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/core.tex
add direction info to captions

\caption{Example: {\tt main}\apt{Needs machine-set diagram.}}
\label{fig:main}
\end{figure}

@@

  \caption{Execution of example up through the return from {\tt f}. In right-hand diagram, addresses increase to the right and
  boxes represent 4-byte words.}

>>>>

\caption{Example: C and assembly code for {\tt main}, and layout of its stack frame; addresses increase to the right and the stadk grows to the left.\apt{Needs machine-set diagram.}}
\label{fig:main}
\end{figure}

@@

  \caption{Execution of example up through the return from {\tt f}. In stack diagram, addresses increase to the right, stack grows to the left, and boxes represent 4-byte words.}
